---
title: "ERA interim example"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Requirements for using the ECMWF API

1. In order to access the ECMWF API you need to [register your own username](https://apps.ecmwf.int/registration/), [agree to licence agreement](https://apps.ecmwf.int/datasets/licences/general/) and [obtain key](https://api.ecmwf.int/v1/key/) from ECMWF before proceeding.

2. You should install conda, create an environment for the ECMWF API client and install `ecmwf-api-client` from a channel e.g. __conda-forge__.

## Define request, download and convert from ncdf to data frame and save
`var` should be a meteorological variable name as a string. Variables are available from two datasets. From NCEP such as: `temperature`,`relative humidity`,`u wind`,`v wind`,`soil heat flux`,`net radiation` or `precipitation rate`. And from [GPCC](http://dx.doi.org/10.5676/DWD_GPCC/FD_D_V2018_100) such as `gpcc precipitation` and `number of gauges`.

### Define request
```{r, results='asis'}
library(scraping)
```

Insert coordinates as points:
```{r, results='asis'}
coor <- data.frame(lon=c(13.40,13.91),lat=c(52.52,52.90))
```
...or as left, right, bottom and top extents of your region of interest:
```{r, results='asis'}
coor <- data.frame(l=12,r=14,b=50,t=53)
```

Choose years and variables
```{r, results='asis'}
vartable$dataset[which(vartable$dataset=='era-interim')] <- 'era5'

getwd()

var <- c('soil heat flux','precipitation rate')
years <- c('2000')
setwd('/home/delgado/proj/scraping')
request <- def_request(coor,var,'ncep',years)
knitr::kable(request)


```

### Download and convert from ncdf to data frame and save
```{r eval=FALSE}

get_nc(request)

nc2rds(request)
```

### Print metadata
```{r, results='asis'}
setwd('/home/delgado/proj/scraping')
get_nc_meta(request,var[2])
get_nc_spatial_res(request)
```


## Load rds data examples

```{r, results='asis'}
library(scraping)
library(dplyr)
library(lubridate)
lookup=lookup_var(request$variable)

lookup %>% knitr::kable()

myproj='/home/delgado/proj/scraping/'

df1=readRDS(paste0(myproj,lookup$varname[1],'.rds'))
df2=readRDS(paste0(myproj,lookup$varname[2],'.rds'))

head(df2) %>% knitr::kable()
```

Compute daily maxima if it applies (for example temperature and relative humidity, not precipitation rate or net radiation, which is given as daily values):

```{r, results='asis'}
df1 %>%
    group_by(day=floor_date(time,"day"),lon,lat) %>%
    summarise(daily_max=max(value),daily_min=min(value),daily_mean=mean(value),var=first(var)) %>%  
    head() %>%
    knitr::kable()
```
