---
title: "ERA interim example"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Requirements for using the ECMWF API

1. In order to access the ECMWF API you need to [register your own username](https://apps.ecmwf.int/registration/), [agree to licence agreement](https://apps.ecmwf.int/datasets/licences/general/) and [obtain key](https://api.ecmwf.int/v1/key/) from ECMWF before proceeding.

2. You should install conda, create an environment for the ECMWF API client and install `ecmwf-api-client` from a channel e.g. __conda-forge__.

__It is important to start the python instance with `reticulate` before loading any other package!!__

## Add parameter to `vartable`

Check [the parameter database of ECMWF](https://apps.ecmwf.int/codes/grib/param-db) and update the existing table with the necessary parameter. Then please be so kind and do a pull request on [my repo](https://github.com/jmigueldelgado/hymet-datasets)

```{r, results='asis'}
library(hymet-datasets)
library(dplyr)

vartext='U component of wind'
varcode='131'
if((vartable %>% filter(variable== vartext) %>% nrow)==0)
  {
    vartable = vartable %>%
      bind_rows(.,data_frame(variable=vartext,varname=varcode,dataset="reanalysis-era5-complete"))
    save(vartable,file='data/vartable.rda')
  }

```

## Define request, download and convert from ncdf to data frame and save
`var` should be a meteorological variable name as a string. Variables are available from two datasets. From NCEP such as: `temperature`,`relative humidity`,`u wind`,`v wind`,`soil heat flux`,`net radiation` or `precipitation rate`. And from [GPCC](http://dx.doi.org/10.5676/DWD_GPCC/FD_D_V2018_100) such as `gpcc precipitation` and `number of gauges`.

### Define request
```{r, results='asis'}
library(hymet-datasets)
library(dplyr)
l=13.40
r=13.80
b=52.20
t=52.80

geom=list(cbind(c(l,r,r,l,l),c(b,b,t,t,b))) %>%
        sf::st_polygon(.) %>%
        sf::st_sfc(.) %>%
        sf::st_sf(.) %>%
        sf::st_set_crs(.,4326)

var= 'temperature'
years <- c('2000')
setwd('/home/delgado/proj/hymet-datasets')


request <- hymet-datasets::def_request(var,geom,years,'reanalysis-era5-complete',levtype='sfc') %>% dplyr::distinct(request,varname,year,.keep_all=TRUE)

request$fname='mydownload'
request$prefix='mydownload'

cds=config_python()
client=cds$Client()
gridsize=0.125

bb=sf::st_bbox(geom)

r_query=list(
  class='ea',
  expver='1',
  stream='oper',
  type='an',
  levtype=as.character(request$levtype),
  param=request$param, # 2m temperature
  # grid=paste0(gridsize,'/',gridsize),
  # area=paste0(bb[4],'/',bb[1],'/',bb[2],'/',bb[3]), # N/W/S/E
  date=paste0(request$year,'-01-01/to/',request$year,'-12-31'),
  time='00/to/23/by/6'
  )

r_query
query = reticulate::r_to_py(r_query)

client$retrieve(request$dataset,query,target=paste0(request$fname,'_',request$year,'.grib'))

get_nc(request)

  ```
