---
title: "ERA interim example"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Requirements for using the ECMWF API

1. In order to access the ECMWF API you need to [register your own username](https://apps.ecmwf.int/registration/), [agree to licence agreement](https://apps.ecmwf.int/datasets/licences/general/) and [obtain key](https://api.ecmwf.int/v1/key/) from ECMWF before proceeding.

2. You should install conda, create an environment for the ECMWF API client and install `ecmwf-api-client` from a channel e.g. __conda-forge__.

__It is important to start the python instance with `reticulate` before loading any other package!!__

## Define request, download and convert from ncdf to data frame and save
`var` should be a meteorological variable name as a string. Variables are available from two datasets. From NCEP such as: `temperature`,`relative humidity`,`u wind`,`v wind`,`soil heat flux`,`net radiation` or `precipitation rate`. And from [GPCC](http://dx.doi.org/10.5676/DWD_GPCC/FD_D_V2018_100) such as `gpcc precipitation` and `number of gauges`.

### Define request
```{r, results='asis'}
library(scraping)

coor <- data.frame(lon=c(13.40),lat=c(52.52))
var= '2 metre temperature'
years <- c('2000')
setwd('/home/delgado/proj/scraping')

request <- scraping::def_request(coor,var,'reanalysis-era5-complete',years)

request_i <- dplyr::distinct(request,varname,year,.keep_all=TRUE)

get_nc(request_i)
```
