---
title: "ERA interim example"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Requirements for using the ECMWF API

1. In order to access the ECMWF API you need to [register your own username](https://apps.ecmwf.int/registration/), [agree to licence agreement](https://apps.ecmwf.int/datasets/licences/general/) and [obtain key](https://api.ecmwf.int/v1/key/) from ECMWF before proceeding.

2. You should install conda, create an environment for the ECMWF API client and install `ecmwf-api-client` from a channel e.g. __conda-forge__.

__It is important to start the python instance with `reticulate` before loading any other package!!__

## Add parameter to `vartable`

Check [the parameter database of ECMWF](https://apps.ecmwf.int/codes/grib/param-db) and update the existing table with the necessary parameter. Then please be so kind and do a pull request on [my repo](https://github.com/jmigueldelgado/scraping)

```{r, results='asis'}
library(scraping)
library(dplyr)

vartext='U component of wind'
varcode='131'
if((vartable %>% filter(variable== vartext) %>% nrow)==0)
  {
    vartable = vartable %>%
      bind_rows(.,data_frame(variable=vartext,varname=varcode,dataset="reanalysis-era5-complete"))
    save(vartable,file='data/vartable.rda')
  }

```

## Define request, download and convert from ncdf to data frame and save
`var` should be a meteorological variable name as a string. Variables are available from two datasets. From NCEP such as: `temperature`,`relative humidity`,`u wind`,`v wind`,`soil heat flux`,`net radiation` or `precipitation rate`. And from [GPCC](http://dx.doi.org/10.5676/DWD_GPCC/FD_D_V2018_100) such as `gpcc precipitation` and `number of gauges`.

### Define request
```{r, results='asis'}
library(scraping)
library(dplyr)
l=13.40
r=13.80
b=52.20
t=52.80

geom=list(cbind(c(l,r,r,l,l),c(b,b,t,t,b))) %>%
        sf::st_polygon(.) %>%
        sf::st_sfc(.) %>%
        sf::st_sf(.) %>%
        sf::st_set_crs(.,4326)

str(geom)
sf::st_bbox(geom)

var= '2 metre temperature'
years <- c('2000')
setwd('/home/delgado/proj/scraping')

request <- scraping::def_request(geom,var,'reanalysis-era5-complete',years)

request_i <- dplyr::distinct(request,varname,year,.keep_all=TRUE)

get_nc(request_i)
```
