---
title: "NCEP example"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Define request, download and convert from ncdf to data frame and save
`var` should be a meteorological variable name as a string such as `temperature`,`relative humidity`,`u wind`,`v wind`,`soil heat flux`,`net radiation` or `precipitation rate`.

### Define request
```{r, results='asis'}
library(scraping)
```

Insert coordinates as points:
```{r, results='asis'}
coor <- data.frame(lon=c(13.40,13.91),lat=c(52.52,52.90))
```
...or as left, right, bottom and top extents of your region of interest:
```{r, results='asis'}
coor <- data.frame(l=12,r=14,b=50,t=53)
```

Choose years and variables
```{r, results='asis'}
var <- c('temperature')
years <- c('2000','2001')
setwd('/home/delgado/proj/scraping')
request <- def_request(coor,var,years)
knitr::kable(request)


```

### Download and convert from ncdf to data frame and save
```{r eval=FALSE}

get_nc(request)

nc2rds(request)

```


## Load rds data examples

### Load air temperature

```{r, results='asis'}
library(scraping)
library(dplyr)
library(lubridate)

var=lookup_var('temperature') %>% pull(varname)

myproj='/home/delgado/proj/scraping/'

df1=readRDS(paste0(myproj,var,'.rds'))

head(df1) %>% knitr::kable()

df1 %>%
    group_by(day=floor_date(time,"day")) %>%
    summarise(daily_max=max(value),daily_min=min(value),daily_mean=mean(value),var=first(var)) %>%  
    head() %>%
    knitr::kable()
```
