---
title: "NCEP example"
author: "JM Delgado"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Define request, download and convert from ncdf to data frame and save
`var` should be a meteorological variable name as a string. Variables are available from two datasets. From NCEP such as: `temperature`,`relative humidity`,`u wind`,`v wind`,`soil heat flux`,`net radiation` or `precipitation rate`. And from [GPCC](http://dx.doi.org/10.5676/DWD_GPCC/FD_D_V2018_100) such as `gpcc precipitation` and `number of gauges`.

### Define request
```{r, results='asis'}
library(scraping)
```

Insert coordinates as points:
```{r, results='asis'}
coor = data.frame(lon=-7.91452, lat=40.65758)
```

Choose years and variables
```{r, results='asis'}
var <- c('era monthly wind')
years <- as.vector( as.character(seq(1970,2010)))
setwd('/home/delgado/proj/scraping')
request <- def_request(coor,var,years)

knitr::kable(request)

```

### Download and convert from ncdf to data frame and save
```{r eval=FALSE}

nc2rds(request)

```

### Print metadata
```{r, results='asis'}
setwd('/home/delgado/proj/scraping')
get_nc_meta(request,var[2])
```


## Load rds data examples

```{r, results='asis'}
library(scraping)
library(dplyr)
library(lubridate)
lookup=lookup_var(request$variable)

lookup %>% knitr::kable()

myproj='/home/delgado/proj/scraping/'

df1=readRDS(paste0(myproj,lookup$varname[1],'.rds'))
df2=readRDS(paste0(myproj,lookup$varname[2],'.rds'))

require(ggplot2)

df1 %>% filter(lon==-7.75,lat==40.75) %>% ggplot(.) + geom_line(aes(x=time,y=value))

head(df2) %>% knitr::kable()
```

Compute daily maxima if it applies (for example temperature and relative humidity, not precipitation rate or net radiation, which is given as daily values):

```{r, results='asis'}
df1 %>%
    group_by(day=floor_date(time,"day"),lon,lat) %>%
    summarise(daily_max=max(value),daily_min=min(value),daily_mean=mean(value),var=first(var)) %>%  
    head() %>%
    knitr::kable()
```
